Coherent optical creation of a single molecule

### 2020-11-25 paper.tex
Clarify relation between lifetime and scattering rate

The efficiency of the transfer is lower than expected
because we found the ratio of the molecular scattering rate to the Rabi frequency
is 10 times larger than predicted. If this discrepancy arises from the $v'=0$ excited state,
it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
Additionally, coupling to other excited states can add an offset to
both the Raman Rabi frequency and the scattering rate and thus affect their ratio.

>>>>

The efficiency of the transfer is lower than expected
because we found the ratio of the molecular scattering rate~(i.e. inverse of lifetime)
to the Rabi frequency is 10 times larger than predicted.
If this discrepancy arises from the $v'=0$ excited state,
it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
Additionally, coupling to other excited states can add an offset to
both the Raman Rabi frequency and the scattering rate and thus affect their ratio.
